---
title: "Airbnb in Amsterdam"
author: "Xiaofan Xia"
date: "12/12/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(factoextra)
library(FactoMineR)
df1 <- read.csv("/Users/XiaofanXia/Desktop/MA615/ma615_final project/airbnb-amsterdam/listings.csv")
df2 <- read.csv("/Users/XiaofanXia/Desktop/MA615/ma615_final project/airbnb-amsterdam/reviews_details.csv")
df1 <- df1[-5]
```

## Introduction
Objective: Finding out the relationship between reviewers’ comments and price regarding to different room type and neighborhood in Amsterdam. 

Deliverables: A report, a presentation, a shiny app.

Dataset: Airbnb Amsterdam from Kaggle. (

Source: https://www.kaggle.com/erikbruin/airbnb-amsterdam.

## Research Questions
1. Is there any relationship between the price and the attitude of reviewers of an Airbnb? 
2. Is there any relationship between the price and the neighborhood of the Airbnb located?
3. Is there any difference in prices regarding different room types of Airbnb?
4. Is there any relationship between the price and the availability of an Airbnb?
5. Generate a shiny app to show locations of Amsterdam’s Airbnb places. 


## Basic Statistics 

```{r echo=FALSE,warning=FALSE,message=FALSE}
# availability 365
aval_max <- max(df1$availability_365) #365
aval_min <- min(df1$availability_365) #0
aval_mean <- mean(df1$availability_365) # 59.91
aval_median <- median(df1$availability_365) #3

# reviews per month
df1$reviews_per_month <- as.numeric(df1$reviews_per_month)
mreview_max <- max(df1$reviews_per_month,na.rm = TRUE) #11.85
mreview_min <- min(df1$reviews_per_month,na.rm = TRUE) #0.01
mreview_mean <- mean(df1$reviews_per_month,na.rm = TRUE) #1.06
mreview_median <- median(df1$reviews_per_month,na.rm = TRUE) #0.62

# number of reviews
df1$number_of_reviews <- as.numeric(df1$number_of_reviews)
treview_max <- max(df1$number_of_reviews,na.rm = TRUE) #695
treview_min <- min(df1$number_of_reviews,na.rm = TRUE) #00
treview_mean <- mean(df1$number_of_reviews,na.rm = TRUE) #21.56
treview_median <- median(df1$number_of_reviews,na.rm = TRUE) #8

# price
df1$price <- as.numeric(df1$price)
price_max <- max(df1$price) #8500
price_min <- min(df1$price) #0
price_mean <- mean(df1$price) #152.18
price_median <- median(df1$price) #125

# minimum of nights
df1$minimum_nights <- as.numeric(df1$minimum_nights)
night_max <- max(df1$minimum_nights) #1001
night_min <- min(df1$minimum_nights) #1
night_mean <- mean(df1$minimum_nights) #3.33
night_median <- median(df1$minimum_nights) #2

aval<- c(aval_max,aval_min,aval_mean,aval_median)
review_month <- c(mreview_max,mreview_min,mreview_mean,mreview_median)
review_total <- c(treview_max,treview_min,treview_mean,treview_median)
price <- c(price_max,price_min,price_mean,price_median)
min_night <- c(night_max,night_min,night_mean,night_median)

stat_df <- data.frame(aval,review_month,review_total,price,min_night)
names(stat_df) <- c("Availability in nights during a year","Number of reviews per month","Number of reviews in total","Price","Minimum nights of stay")
row.names(stat_df) <- c("Maximum","Minimum","Mean","Median")
kable(t(stat_df))

```

## Graph Presentations


## Principal Component Analysis



## Text Analysis
First, I conduct a text analysis on three Airbnb places from each room type (shared room, entire home/apt, and private room). 
