---
title: "Airbnb in Amsterdam"
author: "Xiaofan Xia"
date: "12/12/2019"
output: ioslides_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(factoextra)
library(FactoMineR)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(webshot)
library(htmlwidgets)

options("kableExtra.html.bsTable" = T)
df1 <- read.csv("/Users/XiaofanXia/Desktop/MA615/ma615_final project/airbnb-amsterdam/listings.csv")
#df2 <- read.csv("/Users/XiaofanXia/Desktop/MA615/ma615_final project/airbnb-amsterdam/reviews_details.csv")
df1 <- df1[-5]
share <- 
  df1 %>%
  filter(room_type=="Shared room")
private <- 
  df1 %>%
  filter(room_type=="Private room")
entire <- 
  df1 %>%
  filter(room_type=="Entire home/apt")
#Private room
#room2818 <- df2 %>%filter(listing_id=="2818")
#write.csv(room2818,file="room2818.csv")
#Entire home/apt
#room20168 <-df2 %>%filter(listing_id=="20168")
#write.csv(room20168,file="room20168.csv")
#Shared room
#room760599 <-df2 %>%filter(listing_id=="760599")
#write.csv(room760599,file="room760599.csv")
room_p <- read.csv("room2818.csv")
room_e <- read.csv("room20168.csv")
room_s <- read.csv("room760599.csv")
```

## Introduction
- Objective: Explore the relationship between reviewers’ comments and the  price. 
(All prices in this project are assumed in the same currency and the same unit.)

- Deliverables: A report, a presentation, a shiny app.

- Dataset: Airbnb Amsterdam from Kaggle. (

- Source: https://www.kaggle.com/erikbruin/airbnb-amsterdam.

## Research Questions
1. Is there any relationship between the price and the attitude of reviewers of an Airbnb? 
2. Is there any relationship between the price and the neighborhood of the Airbnb located?
3. Is there any difference in prices regarding different room types of Airbnb?
4. Is there any relationship between the price and the availability of an Airbnb?
5. Generate a shiny app to show locations of Amsterdam’s Airbnb places. 


## Basic Statistics 

```{r echo=FALSE,warning=FALSE,message=FALSE}
# availability 365
aval_max <- max(df1$availability_365) #365
aval_min <- min(df1$availability_365) #0
aval_mean <- mean(df1$availability_365) # 59.91
aval_median <- median(df1$availability_365) #3

# reviews per month
df1$reviews_per_month <- as.numeric(df1$reviews_per_month)
mreview_max <- max(df1$reviews_per_month,na.rm = TRUE) #11.85
mreview_min <- min(df1$reviews_per_month,na.rm = TRUE) #0.01
mreview_mean <- mean(df1$reviews_per_month,na.rm = TRUE) #1.06
mreview_median <- median(df1$reviews_per_month,na.rm = TRUE) #0.62

# number of reviews
df1$number_of_reviews <- as.numeric(df1$number_of_reviews)
treview_max <- max(df1$number_of_reviews,na.rm = TRUE) #695
treview_min <- min(df1$number_of_reviews,na.rm = TRUE) #00
treview_mean <- mean(df1$number_of_reviews,na.rm = TRUE) #21.56
treview_median <- median(df1$number_of_reviews,na.rm = TRUE) #8

# price
df1$price <- as.numeric(df1$price)
price_max <- max(df1$price) #8500
price_min <- min(df1$price) #0
price_mean <- mean(df1$price) #152.18
price_median <- median(df1$price) #125

# minimum of nights
df1$minimum_nights <- as.numeric(df1$minimum_nights)
night_max <- max(df1$minimum_nights) #1001
night_min <- min(df1$minimum_nights) #1
night_mean <- mean(df1$minimum_nights) #3.33
night_median <- median(df1$minimum_nights) #2

aval<- c(aval_max,aval_min,aval_mean,aval_median)
review_month <- c(mreview_max,mreview_min,mreview_mean,mreview_median)
review_total <- c(treview_max,treview_min,treview_mean,treview_median)
price <- c(price_max,price_min,price_mean,price_median)
min_night <- c(night_max,night_min,night_mean,night_median)

stat_df <- data.frame(aval,review_month,review_total,price,min_night)
names(stat_df) <- c("Availability in nights during a year","Number of reviews per month","Number of reviews in total","Price","Minimum nights of stay")
row.names(stat_df) <- c("Maximum","Minimum","Mean","Median")
kable(t(stat_df))

```


## Graph Presentations of Shared Rooms
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(share)+geom_point(aes(price,number_of_reviews,color=neighbourhood))+ggtitle("Shared rooms")+xlab("Price")+ylab("Number of reviews in total")+theme(legend.text = element_text(size=5))
```

## Graph Presentations of Shared Rooms
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(share)+geom_point(aes(price,reviews_per_month,color=neighbourhood))+ggtitle("Shared rooms")+xlab("Price")+ylab("Number of reviews per month")+theme(legend.text = element_text(size=5))
```

## Graph Presentations of Private Rooms
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(private)+geom_point(aes(price,number_of_reviews,color=neighbourhood))+ggtitle("Private rooms")+xlab("Price")+ylab("Number of reviews in total")+xlim(0,1000)+theme(legend.text = element_text(size=5))
```

## Graph Presentations of Private Rooms
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(private)+geom_point(aes(price,reviews_per_month,color=neighbourhood))+ggtitle("Private rooms")+xlab("Price")+ylab("Number of reviews per month")+xlim(0,1000)+theme(legend.text = element_text(size=5))
```

## Graph Presentations of Entire Homes/ Apartments
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(entire)+geom_point(aes(price,number_of_reviews,color=neighbourhood))+ggtitle("Entire home/ apartment")+xlab("Price")+ylab("Number of reviews in total")+theme(legend.text = element_text(size=5))
```

## Graph Presentations of Entire Homes/ Apartments
```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(entire)+geom_point(aes(price,reviews_per_month,color=neighbourhood))+ggtitle("Entire home/ apartment")+xlab("Price")+ylab("Number of reviews per month")+theme(legend.text = element_text(size=5))
```


## Principal Component Analysis



## Text Analysis

- Three Airbnb places from each room types.

- Text analysis for each place.

- Word cloud of comments for each Airbnb. 

- What elements relate to the Airbnb mostly. 

## Shared room
```{r echo=FALSE,message=FALSE,warning=FALSE}
comment_s <- room_s$comments
df_s <-tibble(line=1:46,text=comment_s)
df_s$text <- as.character(df_s$text)
df_s <-
  df_s %>%
  unnest_tokens(output=word,input=text,token="words") %>%
  anti_join(stop_words)
df_s <-
  df_s%>%
  count(word,sort = TRUE)
wc1 <-wordcloud2(df_s,size=0.5,color = "random-light",shape = "circle")
saveWidget(wc1,"wc1.html",selfcontained = F)
webshot::webshot("wc1.html","wc1.png",vwidth = 600, vheight = 400, delay =5)
print(wc1)
```

## Private room
```{r echo=FALSE,message=FALSE,warning=FALSE}
comment_p <- room_p$comments
df_p <-tibble(line=1:248,text=comment_p)
df_p$text <- as.character(df_p$text)
df_p <-
  df_p %>%
  unnest_tokens(output=word,input=text,token="words") %>%
  anti_join(stop_words)
df_p <-
  df_p%>%
  count(word,sort = TRUE)
wc2 <-wordcloud2(df_p,size=1,color = "random-light",shape = "circle")
saveWidget(wc2,"wc2.html",selfcontained = F)
webshot::webshot("wc2.html","wc2.png",vwidth = 600, vheight =400, delay =5)
print(wc2)

```

## Entire homes/ apartments
```{r echo=FALSE,message=FALSE,warning=FALSE}
comment_e <- room_e$comments
df_e <-tibble(line=1:233,text=comment_e)
df_e$text <- as.character(df_e$text)
df_e <-
  df_e %>%
  unnest_tokens(output=word,input=text,token="words") %>%
  anti_join(stop_words)
df_e <-
  df_e%>%
  count(word,sort = TRUE)
wc3 <- wordcloud2(df_e,size=0.8,color = "random-light",shape = "circle")
saveWidget(wc3,"wc3.html",selfcontained = F)
webshot::webshot("wc3.html","wc3.png",vwidth = 600, vheight = 400, delay =5)
print(wc3)
```


## Conclusion and Discussion

